---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# MTMC-SKAT

<!-- badges: start -->
<!-- badges: end -->

MTMC-SKAT provides high-level R and command line interfaces for SKAT, most notably with support for multi-threaded adaptive resampling to rapidly calculate empirical p-values. Resampling is performed using an algorithm that allows calculation of empirical p-values to a user-specified number of significant figures. The efficiency of parallelization over SNP windows or permutations depends on a given dataset and resources of a given computer. In the automated workflow, permutations are continually generated and batches of SNP windows are tested to calculate empirical p-values as sufficient permutations become available for each batch. The appropriate mode (multithreading over windows or permutations) is automatically detected for each batch of SNP windows. See the MTMC-SKAT Workflows vignette for details on this automatic workflow and information for designing custom workflows.

Workflows are applied over scaffolds independently, with parallelization over scaffolds or sub-scaffolds on high-performance clusters as described later. Each scaffold is submitted as a .traw file, which can be prepared from more common SNP data formats using PLINK. The standard workflow can be run over a given scaffold using the following command.

```{r cars}
#summary(cars)
```

This function is also accesible from the command line, thus providing a one-liner that can be easily submitted as a job to any batch query system.

Finally, the following function can be used to generate a bash script to submit an array of jobs (each for a given scaffold or sub-scaffold) to be submitted to to the SGE or SLURMS batch query system.

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
#plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
